JuliaCon Proceedings in Quarto

### 2024-01-08 examples/CounterfactualExplanations.jl/paper.tex
going to turn the presentation into a website

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, boxrule=0pt, sharp corners, interior hidden, frame hidden, breakable, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, interior hidden, sharp corners, enhanced, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, frame hidden]}{\end{tcolorbox}}\fi

### 2024-01-08 template.qmd
going to turn the presentation into a website

Support for executable listings is only available in the development version of Quarto (version $\geq$ 1.4.0). It is currently not clear how to support custom formatting, for example through the existing `jlcode.sty` environment.

@@

Markdown tables are rendered to LaTeX using the `booktabs` package. This is the recommended way to create tables because it is compatible with various output formats. Tables can be cross-referenced and the table caption will be rendered as a LaTeX table caption.

@@

<!-- | Default | Left | Right | Center |
|---------|:-----|------:|:------:|
| 12      | 12   |    12 |   12   |
| 123     | 123  |   123 |  123   |
| 1       | 1    |     1 |   1    |

: Demonstration of pipe table syntax {#tbl-1} -->

@@

Standard LaTeX syntax can also be used to create tables. To use standard Quarto cross-referencing, the LaTeX syntax needs to be wrapped in a `div` with the `tbl` class. The table caption can be added as a paragraph. The following creates @tbl-1 which can be cross-referenced as `@tbl-1`.

```
::: {#tbl-1}

@@

::: {#tbl-1}

@@

>>>>

- Support for executable listings is only available in the latest version of Quarto (version $\geq$ 1.4.0).
- It is currently not clear how to support custom formatting, for example through the existing `jlcode.sty` environment. 
- Cross-referencing listings does not seem to work in HTML output.

@@

Markdown tables are rendered to LaTeX using the `booktabs` package. This is the recommended way to create tables because it is compatible with various output formats. Tables can be cross-referenced as `@tbl-1` which renders as @tbl-1.

@@

@@

Standard LaTeX syntax can also be used to create tables. To use standard Quarto cross-referencing, the LaTeX syntax needs to be wrapped in a `div` with the `tbl` class. The table caption can be added as a paragraph. The following creates @tbl-2 which can be cross-referenced as `@tbl-2`.

```
::: {#tbl-2}

@@

::: {#tbl-2}

@@

# Citations

This `@altmeyer2023endogenous` renders the citation as @altmeyer2023endogenous. The bibliography is defined in `bibliography.bib`.

# References
